Report on Late Winter2013 Production: Image Differencing

### 2013-03-29 W13report.tex
Debugging of stats section.

\subsubsection{Mean Squared Error}

In order to investigate the bias--variance trade--off in the overall
fit, we calculate the MSE of each {\tt KernelCandidate's} difference
image derived from the evaluation of the spatial model at that
location.  We define the bias as $\left| data - model \right|$, the
variance as $\left| (data - model)^2 \right|$, and the MSE as {\tt
  bias$^2$ + variance}.  In this context, the bias is the mean of the
difference image, and the variance is the mean square of the
difference image.  In both cases, we normalize by the square root of
the variance so that pixels are in units of sigma.

Ideally, the MSE gives a means for identifying the location in parameter 
space of optimal fitting without overfitting.  We calculated the median MSE
for all {\tt KernelCandidates} in each of the test configs.  For each config
we have two sets of {\tt KernelCandidates}.  The first is the FITTED sample and
includes all {\tt KernelCandidates} used to fit the kernel and spatial models.  The second,
the CONTROL sample, is a set of {\tt KernelCandidates} held out of the fitting
to use as a cross validation sample of the models.

In each case there is a minimum in the measured MSE of the CONTROL sample suggesting
that the test configs span a sufficient range of complexity in the parameter space to 
go from under to over fitting.  Table \ref{tab-bestconfig_MSE}.

\subsubsection{Reduced $\chi^2$}

@@

\clearpage
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
\hline
Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
\hline
R22:S00&4.2&5.8&3.8&382\\ 
R22:S10&2.6&4.4&4.4&389\\
R22:S20&1.4&3.6&4.2&375\\
R22:S01&2.6&5.0&4.2&86\\
R22:S11&1.2&3.4&4.0&81\\
R22:S21&1.6&3.8&4.0&382\\
R22:S02&1.6&3.4&4.0&178\\
R22:S12&1.8&4.0&4.0&78\\
R22:S22&1.4&4.2&4.2&389\\
\hline
\end{tabular}
\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the reference catalog, the science exposure to the reference catalog,
fitting the deep exposure directly to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point.\label{tab-wcsrms}}
\end{table}
\clearpage

>>>>

We implemented several diagnostics on the quality of the image
subtractions for a given {\tt KernelCandidate}.  This was done for the
original $T_j(x,y)$ to $S_j(x,y)$ kernel fit, yielding LOCAL quality
statistics.  These were re--evaluated using the spatial kernel model
$K(u,v,x_j,y_j)$ evaluated at the {\tt KernelCandidate} location,
yielding SPATIAL quality statistics.  The task metadata was augmented
with summary statistics of these values (mean, median, RMS), and the
information on each {\tt KernelCandidate} persisted in a new {\tt
  kernelSrc} data product.  We briefly describe more useful of these
statistics below.

The first statistic, KCDiffimStDev, measures the standard deviation of
all the non--{\tt EDGE} pixels in the difference image, normalized by
the sqrt of the variance in the difference image.  In the idealized
case, this value should be 1.0, i.e. pixels in the image are drawn
from a normal (0,1) distribution.  In cases of overfitting or
underfitting, this value will be lower than / higher than 1.0.

We also calculate a reduced $\chi^2_\nu$ value called KCDiffimChiSq.
The numerator of this term is the sum of the squares of the
noise--normalized pixel values.  This sum is normalized by the number
of pixels in the data, minus the number of basis shapes in the kernel
plus 1.

Finally in order to investigate the bias--variance trade--off in the
overall fit, we calculate the mean square error (MSE) of each {\tt
  KernelCandidate's} difference image as statistic KCDiffimMseResids.
We define the bias as $\left| data - model \right|$, the variance as
$\left| (data - model)^2 \right|$, and the MSE as {\tt bias$^2$ +
  variance}.  In this context, the bias is the mean of the difference
image, and the variance is the mean square of the difference image.
Ideally, the MSE gives a means for identifying the location in
parameter space of optimal fitting without overfitting.

For all statistics, we have a FITTED sample, which are the {\tt
  KernelCandidates} that were used to derive the spatial model.
Importantly we also have a CONTROL sample of {\tt KernelCandidates}
that were explicitly held out of the fitting to use as a cross
validation sample.

{\bf MOVE ME}
In each case there is a minimum in the measured MSE of the CONTROL sample suggesting
that the test configs span a sufficient range of complexity in the parameter space to 
go from under to over fitting.  Table \ref{tab-bestconfig_MSE}.

@@

\clearpage
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
\hline
Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
\hline
R22:S00&4.2&5.8&3.8&382\\ 
R22:S10&2.6&4.4&4.4&389\\
R22:S20&1.4&3.6&4.2&375\\
R22:S01&2.6&5.0&4.2&86\\
R22:S11&1.2&3.4&4.0&81\\
R22:S21&1.6&3.8&4.0&382\\
R22:S02&1.6&3.4&4.0&178\\
R22:S12&1.8&4.0&4.0&78\\
R22:S22&1.4&4.2&4.2&389\\
\hline
\end{tabular}
\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the reference catalog, the science exposure to the reference catalog,
fitting the deep exposure directly to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point. {\bf SIMON MAKE SURE NUMBERS ARE STRAIGHT}\label{tab-wcsrms}}
\end{table}
\clearpage
